\abstract{ \par This thesis is proposed to serve as a concise and to-the-point report of my work in the domain of autonomous navigation of UAVs (Unmanned Aerial Vehicles) and UGVs (Unmanned Ground Vehicles). A driver or operator is generally required to operate a ground vehicle (car, bus, etc.) or an aerial vehicle (quad-copter, etc.). These operators/drivers must be trained, and obtaining a license is also a tedious process (especially for aerial vehicles). In reality, these factors prevent us from utilizing these machines to their full potential and exploring their wide array of valuable applications. 
\par By automating ground vehicles, we could save on fuel, reduce accident-related costs, and improve overall transportation efficiency. An autonomous aerial vehicle, on the other hand, can be used for many purposes, including: Food and medical delivery in remote areas, Public safety in calamities, Bridge and power lines inspection, Agriculture, Road accident report, Traffic monitoring, and Transportation.
\par The main objective is to enable the UAVs to realize autonomous flight control, autonomous object tracking and obstacle avoidance with high accuracy. In order to achieve our goals, I have done few projects related to autonomous navigation. 
\par Chapter 1 starts with basic micro-controllers which we have used in our projects. Chapter 2 defines the UAVs i.e, how flight dynamics works and which controllers and sensors are used to fly our drones or quad-copters. In chapter 3, we discussed a indoor navigation problem i.e, Beacon tracking using ESP32 and Raspberry Pi. This problem has been solved by two methods. We also compared these two methods one is moving average and other is Machine Learning based approach. In chapter 3, we implemented an application of lane detection using a simple approach i.e, Hough Transform algorithm on our UGV kit using Raspberry Pi as a main micro-controller.}
